%-------------------------
% Resume in Latex
% Author : Sahil Kumar
% Based on sb2nov/resume template
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\normalsize{#1}}
\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------


    \begin{center}
        \textbf{\Huge \scshape Sahil} \\ \vspace{4pt}
        \normalsize Software Engineer with 8+ years of experience in building distributed backend systems and cloud solutions \\ \vspace{6pt}
        \small
        \faIcon{envelope} \href{mailto:sahil.inbox@icloud.com}{sahil.inbox@icloud.com} \quad $|$ \quad
        \faIcon{phone} +91-8447476029 \quad $|$ \quad
        \faIcon{linkedin} \href{https://linkedin.com/in/sahil1012}{sahil1012} \quad $|$ \quad
        \faIcon{github} \href{https://github.com/sahilkumar1012}{sahilkumar1012}
    \end{center}


%-----------EXPERIENCE-----------


    \section{Experience}
    \resumeSubHeadingListStart

    \resumeSubheading
    {Google}{Feb 2024 -- Dec 2024}
    {Software Engineer III}{Pune, India}
    \resumeItemListStart
    \resumeItem{Integrated \textbf{VPCSC (Virtual Private Cloud Service Controls)} to secure Bare Metal infrastructure for \textbf{VMware on Google Cloud}, restricting access to authorized VPCs only.}
    \resumeItem{Implemented networking features to \textbf{secure customer VPCs}, ensuring all traffic stays within the customer's VPC and preventing any calls from going outside or entering from external networks.}
    \resumeItemListEnd



    \resumeSubheading
    {Amazon Development Centre Pvt. Ltd.}{Jul 2022 -- Dec 2023}
    {Software Development Engineer II}{Bangalore, India}
    \resumeItemListStart
    \resumeItem{Designed and implemented \textbf{AI-powered semantic search} for app/game discovery using transformer-based models and vector embeddings, improving search relevance and user experience.}
    \resumeItem{Enabled \textbf{contextual query understanding}, allowing natural language searches (e.g., “top movie watching apps”) and increasing user engagement.}
    \resumeItem{Led the \textbf{NAWS migration of Amazon Creator}, transitioning the application to a modern Native AWS Architecture.}
    \resumeItem{Leveraged \textbf{AWS Fargate} and multiple AWS native services to improve \textbf{scalability, performance, and cost-efficiency}, ensuring minimal disruption during migration.}
    \resumeItemListEnd



    \resumeSubheading
    {Adobe Inc.}{Mar 2021 -- May 2022}
    {Member of Technical Staff II}{Noida, India}
    \resumeItemListStart
    \resumeItem{\textbf{Led the migration of CPF Engine} from a legacy C++ implementation to a modern Java-based framework, improving \textbf{maintainability, performance, and scalability} of critical PDF operations.}
    \resumeItem{Migrated and optimized the \textbf{Export PDF Worker}, responsible for handling premium PDF operations including \textbf{exporting PDFs to Office formats}, ensuring high \textbf{reliability} and \textbf{efficiency} for all premium document workflows.}
    \resumeItem{Collaborated with cross-functional and external teams, including \textbf{Microsoft}, to implement modular architecture and manage base images, enabling faster feature rollouts and enhanced \textbf{system reliability}.}
    \resumeItemListEnd



    \resumeSubheading
    {STMicroelectronics Pvt. Ltd.}{Jan 2017 -- Mar 2021}
    {Software Developer}{Noida, India}
    \resumeItemListStart
    \resumeItem{Worked in the in-house IT, developing and maintaining enterprise applications supporting multiple business domains.}
    \resumeItem{Engineered critical changes in the \textbf{PRMIS application}, responsible for STMicroelectronics product data, \textbf{product classifications}, and metadata, improving data accuracy and operational efficiency.}
    \resumeItemListEnd


    \resumeSubHeadingListEnd


%-----------EDUCATION-----------


    \section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
    {YMCA University of Science and Technology, Faridabad}{Aug 2013 -- Jun 2017}
    {Bachelor of Technology, Computer Engineering \quad \textbf{CGPA: 8.01/10}}{}
    \resumeSubHeadingListEnd

%-------------------------------------------


%-----------SKILLS-----------


    \section{Skills}\vspace{-0.3cm}
    \begin{multicols}{2}
        \setlength{\columnsep}{0.5cm} % adjust spacing between columns
        \textbf{Core:}
        Data Structures \& Algorithms, Problem Solving, System Design \& Architecture, OOP\\[0.1cm]

        \textbf{Languages:}
        Java, C/C++, Go, Python, SQL\\[0.1cm]

        \textbf{Frameworks \& Tools:}
        Spring Boot, Struts, JSP, Hibernate, React, Angular, ExtJS, Docker, Git\\[0.1cm]

        \textbf{Databases:}
        MySQL, MongoDB, Redis, Amazon Redshift, Firebase\\[0.1cm]

        \textbf{Cloud:}
        AWS, GCP
    \end{multicols}


\end{document}
